intro

### 2022-08-05 06_Paper/ER-ED/ERED_Stage2/method.Rmd
past tense

library(papaja)     # APA conform output
library(readxl)     # import excel files
```

@@

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK50012022). 
Prior to testing, written informed consent will be obtained.
Participants will receive 30 € in total or course credit for participation.

@@

Young healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE*[@Greiner2015] at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
The second session will take place exactly one week after session one.
Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training will ensure that all participants are able to implement the ER strategies.
Next, electrodes to measure facial EMG will be attached and the ER task will be conducted, followed by an ED procedure regarding the ER strategies.
After that, participants will choose one ER strategy to repeat one more time.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].

@@

The online survey will contain a number of questionnaires. 
In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
It assesses flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which we define as ER flexibility. 
The items are rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".

Further psychological constructs will be assessed but have no clear hypotheses in the present work and are therefore investigated only exploratory:
General psychological well-being will be assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
To assess Need for Cognition, the German version short form of the Need for Cognition Scale[@Cacioppo1982; @Bless1994] will be used.
To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)[@Schwarzer1999], the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011].
Attentional control will be assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).

@@

The ER paradigm will consist of three parts that will be described in the following.

>>>>

#library(papaja)     # APA conform output
#library(readxl)     # import excel files
```

@@

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK50012022). 
Prior to testing, written informed consent was obtained.
Participants received 24 € in total or course credit for participation.

@@

Young healthy participants (aged 18 to 30 years) were recruited using the software *ORSEE*[@Greiner2015] at the Technische Universität Dresden.
Participants were excluded from participation if they do not fluently speak German, had current or a history of psychological disorders or neurological trauma, or reported to take medication.
Participants were invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consisted of two lab sessions, which took place in a shielded cabin with constant lighting.
Before each session, participants received information about the respective experimental procedure and provided informed consent.
In the first session participants filled out a demographic questionnaire and completed an *n*-back task with the levels one to four.
Then, they completed an effort discounting (ED) procedure regarding the *n*-back levels on screen, followed by a random repetition of one *n*-back level [@ZernaScheffel2022].
The second session took place exactly one week after session one.
Participants provided informed consent and received written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensured that all participants were able to implement the ER strategies.
Next, electrodes to measure facial EMG were attached and the ER task was conducted, followed by an ED procedure regarding the ER strategies.
After that, participants chose one ER strategy to repeat one more time.
Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].

@@

The online survey contained a number of questionnaires. 
In the focus of the current project was the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
It assesses flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which we define as ER flexibility. 
The items were rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".

Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
General psychological well-being was assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] was used.
Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
To assess Need for Cognition, the German version short form of the Need for Cognition Scale[@Cacioppo1982; @Bless1994] was used.
To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)[@Schwarzer1999], the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011].
Attentional control were assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).

@@

The ER paradigm consisted of three parts that will be described in the following.
